---
title: "assignment4"
author: "Claire Wang"
date: "9/17/2020"
output:
  pdf_document:
    toc: yes
  html_document:
    theme: yeti
    toc: yes
    toc_float: yes
---

## This assignment is to use network data to find walkshed, bikeshed and motorized-shed.


```{r setup, message=F}
library(osmdata)
library(opentripplanner)
library(tidyverse)
library(sf)
library(ggthemes)
library(ggspatial)
library(reshape2)
```

```{r, message=FALSE}

MA_state_plane <- "+proj=lcc +lat_1=41.71666666666667 +lat_2=42.68333333333333 +lat_0=41 +lon_0=-71.5 +x_0=200000 +y_0=750000 +ellps=GRS80 +units=m +no_defs"

publicschool<- st_read("http://bostonopendata-boston.opendata.arcgis.com/datasets/1d9509a8b2fd485d9ad471ba2fdb1f90_0.kml?outSR=%7B%22latestWkid%22%3A2249%2C%22wkid%22%3A102686%7D",quiet = TRUE) 

hospital <-st_read("http://bostonopendata-boston.opendata.arcgis.com/datasets/8f1e5741a4ee4c0f82925d17aab3c002_2.kml?outSR=%7B%22latestWkid%22%3A2249%2C%22wkid%22%3A102686%7D", quiet = TRUE) 

openspace <-st_read("http://bostonopendata-boston.opendata.arcgis.com/datasets/2868d370c55d4d458d4ae2224ef8cddd_7.kml", quiet = TRUE) 

nhoods <- st_read("http://bostonopendata-boston.opendata.arcgis.com/datasets/3525b0ee6e6b427f9aab5d0a1d0a1a28_0.kml", quiet = TRUE) %>% 
  filter (Name== "Charlestown" | 
          Name == "South Boston Waterfront" | 
          Name== "South Boston" )  


publicschool <- publicschool[nhoods,] %>%
  st_join(nhoods)

hospital<- hospital[nhoods,] %>%
  st_join(nhoods)

openspace<- openspace[nhoods,] %>%
  st_join(nhoods)
```

```{r, message=FALSE}
boston_street_features <- opq(bbox = 'Boston MA USA') %>%
  add_osm_feature(key = 'highway') %>%
  osmdata_sf()

boston_streets <- boston_street_features$osm_lines %>%
  st_transform(crs = MA_state_plane)

ggplot(boston_streets) +
  geom_sf() +
  theme_map()
 
```

```{r,message=FALSE,warning=F,results="hide"}
path_otp <- otp_dl_jar("OTP")

path_data <- file.path(getwd(), "OTP")
path_otp <- paste(path_data, "otp.jar",sep = "/")

otp_build_graph(otp = path_otp, dir = path_data, memory = 1024) 
otp_setup(otp = path_otp, dir = path_data, memory =1024)
otpcon <- otp_connect()

```

```{r, message=F,results='hide'}
iso_10min_walk <- 
  otp_isochrone(otpcon = otpcon, fromPlace = publicschool, 
                mode = "WALK", cutoffSec = 600) %>%
  st_transform(crs = MA_state_plane) %>%
  mutate(mode = "walk")

iso_10min_drive <- 
  otp_isochrone(otpcon = otpcon, fromPlace = publicschool, 
                mode = "CAR", cutoffSec = 600) %>%
  st_transform(crs = MA_state_plane) %>%
  mutate(mode = "drive")

iso_all_modes <- rbind(iso_10min_drive, iso_10min_walk)

otp_stop()
```
# Map of Public Schools & Area that is reachable within 10 minutes
This graph shows how public schools are spatially distributed in Charlestown and South Boston. The yellow region is the 10 minute reach on foot and the purple is 10 min reach by car. It looks like both towns have public schools within 10-min drive from anywhere in the town. But Charlestown is better covered by walking distance isochrones.

```{r,message=F, fig.size=10}
right_side <- st_bbox(iso_all_modes)$xmax
left_side  <- st_bbox(iso_all_modes)$xmin
top_side <- st_bbox(iso_all_modes)$ymax
bottom_side <- st_bbox(iso_all_modes)$ymin

ggplot(iso_all_modes) +
  annotation_map_tile(zoomin = 0, type = "cartolight", progress = "none") +
  geom_sf(aes(fill = mode), alpha = 0.5) +
  coord_sf(xlim = c(left_side, right_side), 
           ylim = c(bottom_side, top_side), expand = FALSE) +
  scale_fill_viridis_d(name = "Public Schools & Area that is reachable within 10 minutes",
                       labels = c("By car", "By foot")) +
  theme_map() +
  labs(caption = "Basemap Copyright OpenStreetMap contributors")
```


# Area of 10 min walk from public schools in relation to that of 10-min drive

This graph shows the distribution of area of walk against that of driving. There is no clear pattern of correlation.

```{r,message=F}
iso_areas <- iso_all_modes %>%
  mutate(area = st_area(iso_all_modes)) %>%
  st_set_geometry(NULL) %>%
  pivot_wider(names_from = mode, values_from = area) 

ggplot(iso_areas, 
       aes(x = as.numeric(walk), y = as.numeric(drive))) +
  geom_point() +
  scale_x_continuous(name = 
            "Area within a five-minute walking distance\nof a public school\n(square km)") +
  scale_y_continuous(name = 
            "Area within a five-minute driving distance\nof a public school\n(square km)",breaks = breaks <- seq(0, 8000000, by = 1000000),
            labels = breaks / 1000000) +
  theme_bw()
```


# Distribution Area of isocrone from public schools 

This graph shows the distribution of area of isocrones. The walking isocrone is smaller than that of driving and is also has a smaller variance.


```{r}

new_iso_areas <- melt(iso_areas,
    measure.vars=c("walk", "drive"),
    variable.name="mode",
    value.name="area")

new_iso_areas <- new_iso_areas %>%  mutate(area = as.numeric(area))
ggplot(new_iso_areas , aes(x = mode, y = area/1000000)) +  
  geom_violin(aes(fill=mode),alpha=0.5) +
  geom_point(position = "jitter",
             alpha = 0.5,
             size = 0.5
             ) +
  scale_x_discrete(name = "mode",
                       labels = c("walk",
                                  "drive"
                                  ), ) +
  scale_y_continuous(name = "area"
                  ) +
  ggtitle("Area within a ten-minute distance\nof a public school\n(square km) ")+
  theme_light() +
  theme(legend.position = "below")

```

