---
title: "assignment2"
author: "Claire Wang"
date: "9/17/2020"
output:
  html_document:
    theme: yeti
    toc: true
    toc_float: true
---
##This assignment is to create a map of South America using three types of projection. Estimated GDP of the country in million dollar (md_GDP_est) is used for the variable of analysis.
<br/>


```{r setup, include=FALSE}
library(ggplot2)
library(sf)
library(rnaturalearth)
library(tidyverse)
library(ggspatial)
library(cartogram)
library(ggthemes)
```

```{r}
world <- ne_countries(scale = 50, returnclass = "sf") 

world_map <- ggplot(world) +
  geom_sf() +
  theme_bw()

sa_countries <- world %>%
  filter(continent == "South America")

sa_map <- ggplot(sa_countries) +
  geom_sf() + 
  theme_bw()

sa_map

```

##projections:
1. mexicolcc:SR-ORG:39: Mexico Lambert Conical Conformal<br/>
2. saed:ESRI:102033: South America Albers Equal Area Conic<br/>
3. salcc: ESRI:102015: South America Lambert Conformal Conic<br/>
4. saea:ESRI:102033: South America Albers Equal Area Conic<br/>
<br/>

```{r}
mexicolcc <- "+proj=lcc +lat_1=17.5 +lat_2=29.5 +lat_0=12 +lon_0=-102 +x_0=2500000 +y_0=0 +ellps=WGS84 +units=m +no_defs"

salcc <- "+proj=lcc +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs"
saea <- "+proj=aea +lat_1=-5 +lat_2=-42 +lat_0=-32 +lon_0=-60 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs"
saed <- "+proj=eqdc +lat_0=0 +lon_0=0 +lat_1=-5 +lat_2=-42 +x_0=0 +y_0=0 +ellps=aust_SA +units=m +no_defs"
```
##Map 1:
1. projection:SR-ORG:39: Mexico Lambert Conical Conformal
<br/>

```{r}
sa_transformed0 <- sa_countries %>%
  st_transform(crs = mexicolcc)

ggplot(sa_transformed0) +
  geom_sf() +
  coord_sf(crs = mexicolcc) +
  theme_wsj()

```
##Map 2:
1. projection: ESRI:102033: South America Albers Equal Area Conic
<br/>

```{r}
sa_transformed1 <- sa_countries %>%
  st_transform(crs = salcc)

ggplot(sa_transformed1) +
  geom_sf() +
  geom_sf_label(aes(label=sov_a3),label.r = unit(0.15, "lines"),
  label.size = 0.2
  )+
  coord_sf(crs = salcc) +
  theme_dark()

```
```{r}
ggplot(sa_transformed1, aes(fill = gdp_md_est)) +
  geom_sf(color = NA) +
  geom_sf_label(aes(label=sov_a3),label.r = unit(0.15, "lines"),
  label.size = 0.2
  )+
  scale_fill_viridis_c(
    name = "GDP estimate (Million Dollar)",
    breaks = seq(0, 2000000, by = 150000),
    labels = formatC(seq(0, 2000000, by = 150000), 
                     big.mark = ",", format = "f", digits = 0)) +
    coord_sf(crs = salcc) +
  theme_map() +
  theme(legend.background = element_blank())
```
##Map 3:
1. projection: ESRI:102015: South America Lambert Conformal Conic
<br/>
```{r}
sa_transformed2 <- sa_countries %>%
  st_transform(crs = saea)

ggplot(sa_transformed2) +
  geom_sf() +
  coord_sf(crs = saea
           ) +
  theme_stata()

```
```{r}
cartogram_ncont <- sa_transformed2 %>%
  cartogram_ncont("gdp_md_est")

ggplot(cartogram_ncont, aes(fill = gdp_md_est)) +
  geom_sf(color = NA) +
  geom_sf_text(aes(label=sov_a3),label.r = unit(0.15, "lines"),
  label.size = 0.2
  )+
  scale_fill_viridis_c(
    name = "GDP estimate (Million Dollar)",
    breaks = seq(seq(0, 2000000, by = 150000)),
    labels = formatC(seq(0, 2000000, by = 150000), 
                     big.mark = ",", format = "f", digits = 0)) +
  theme_map() +
  theme(legend.background = element_blank())
```
##Map 4:
1. projection: ESRI:102033: South America Albers Equal Area Conic
<br/>
```{r}
sa_transformed3 <- sa_countries %>%
  st_transform(crs = saed)

ggplot(sa_transformed3) +
  geom_sf() +
  coord_sf(crs = saed) +
  theme_minimal()

```

```{r}
cartogram_dorling <- sa_transformed3 %>%
  cartogram_dorling("gdp_md_est")

ggplot(cartogram_dorling, aes(fill = gdp_md_est)) +
  geom_sf(color = NA) +
   geom_sf_text(aes(label=sov_a3),label.r = unit(0.15, "lines"),
  label.size = 0.2
  )+
  scale_fill_viridis_c(
    name = "GDP estimate (Million Dollar)",
    breaks = seq(0, 2000000, by = 150000),
    labels = formatC(seq(0, 2000000, by = 150000), 
                     big.mark = ",", format = "f", digits = 0)) +
  theme_map() +
  theme(legend.background = element_blank())
```

