---
title: "assignment3"
author: "Claire Wang"
date: "9/24/2020"
output:
  html_document:
    theme: yeti
    toc: true
    toc_float: true
---
<br/>
<br/>
##This assignment is to create 6 maps of Singapore. The two point layers are recycle bins and Singapore Police Force Mobile Speed Cameras, and skyline greenery. The two polygon layers are Singapore Residents by Planning Area and Type of Dwelling and Parks and tree conservation area.

Source:https://data.gov.sg/dataset/
variables:
https://data.gov.sg/dataset/singapore-police-force-mobile-speed-cameras?resource_id=4ddfb2f8-9192-4561-b723-d6af2925060a
https://data.gov.sg/dataset/recycling-bins?resource_id=895f1883-d3bf-467c-833c-226ad92c6229
https://data.gov.sg/dataset/singapore-residents-by-planning-area-and-type-of-dwelling-june-2014?resource_id=622936e8-8596-4489-8eb6-da8703c606c1
https://data.gov.sg/dataset/sdcp-park?resource_id=7cdb6581-f193-440d-b55a-c6d6a44b03a3
https://data.gov.sg/dataset/tree-conservation-area
<br/>
<br/>
```{r, message=FALSE}
library(sf)
library(tidyverse)
library(ggthemes)
library(ggspatial)
library(units)
library(nngeo)
```

```{r, message=F}
respop <- st_read("/Users/clara/OneDrive - Harvard University/singapore-residents-by-planning-area-and-type-of-dwelling-june-2014/PLAN_BDY_DWELLING_TYPE_2014.kml",  quiet = TRUE) 

park<- st_read("/Users/clara/OneDrive - Harvard University/G_MP08_PARKS_PL.kml",  quiet = TRUE)

rebin <- st_read("/Users/clara/OneDrive - Harvard University/recycling-bins/RECYCLINGBINS.kml",  quiet = TRUE) 

rebin1 <- st_read("/Users/clara/OneDrive - Harvard University/recycling-bins/RECYCLINGBINS.kml",  quiet = TRUE) 

speedcam <- st_read("/Users/clara/OneDrive - Harvard University/singapore-police-force-mobile-speed-cameras/SPF_MSC.kml",   quiet = TRUE) 

treec <- st_read("/Users/clara/OneDrive - Harvard University/tree-conservation-area-kml.kml", quiet = TRUE)

skylinegreen <-st_read("/Users/clara/OneDrive - Harvard University/skyrise-greenery/SKYRISEGREENERY.kml",quiet=T)

skylinegreen1 <-st_read("/Users/clara/OneDrive - Harvard University/skyrise-greenery/SKYRISEGREENERY.kml",quiet=T)

sg <- "+proj=utm +zone=48 +ellps=WGS84 +units=m +no_defs "

respop <- respop %>%
  st_transform(sg)

skylinegreen1 <- skylinegreen1 %>%
  st_transform(sg)

park <- park %>%
  st_transform(sg)

rebin <- rebin %>%
  st_transform(sg)
rebin1 <- rebin %>%
  st_transform(sg)

speedcam <- speedcam %>%
  st_transform(sg)

skylinegreen <- skylinegreen%>%
  st_transform(sg)

treec <- treec %>%
  st_transform(sg)
```


```{r, message=F}
ggplot(respop) +
  geom_sf(fill = "lightgrey", color = "white") +
  geom_sf(data = park, fill = "darkgreen",alpha=0.5,color=NA) +
  geom_sf(data = rebin, color="lightblue", fill=NA,size = 0.01) +
  geom_sf(data= speedcam, fill = NA, color = "gray") +
  geom_sf(data=treec,fill="lightgreen",alpha=0.5,color=NA)+
  geom_sf(data=skylinegreen, color="lightyellow",fill=NA,size=0.01)+
  theme_map() +
  annotation_scale()
```
</br>
</br>
1. The number of skyline greenery within 100 m of recycle bins is 112, which is 29% of skyline greeneries.
</br>
</br>

```{r}
rebin_buffer <- st_buffer(rebin, dist = 100) %>%
  st_union()

sk_bin <- skylinegreen[rebin_buffer,]
 
skylinegreen <- skylinegreen %>%
  st_join(sk_bin) %>%
   mutate(by_bins = !is.na(Name.y))

n_sky_bin <- sum(skylinegreen$by_bins)

n_sky_bin

n_sky <- length(skylinegreen$by_bins)

pct_sky_bins <- n_sky_bin/ n_sky

pct_sky_bins

left_side  <- st_bbox(skylinegreen)$xmin
top_side <- st_bbox(skylinegreen)$ymax

ggplot(respop) +
  geom_sf(fill = "lightgrey", color = "white") +
  geom_sf(data=rebin_buffer, fill="lightblue",alpha=0.5)+
  geom_sf(data = skylinegreen, size = 0.01,
          aes(color = by_bins)) +
  scale_color_manual(values = c("lightgreen", "darkgreen"),
          name = "Singapore skyline greeneries by or not by recycle bins", 
          labels = c("No recycle bins within 500m",
                     "recycle bins within 500m")) +
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
  annotate(geom = "text", x = left_side, 
           y = top_side, 
           label = paste("Of the ", 
                         prettyNum(n_sky, big.mark = ","),
                         "skyline greeneries in Singapore", 
                         prettyNum(n_sky_bin, big.mark = ","),
                         " (", 
                         prettyNum(100*pct_sky_bins, digits = 0),
                         "%) are within 100\nmeters of a parking meter.",
                         sep = ""),
           hjust = 0, vjust = 0, size = 3) +
  theme_map() +
  theme(panel.background = element_rect(fill = "white"),
        legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))
```

</br>
</br>
2. The number of recycle bins in the neighborhood.
</br>
</br>
```{r}
respop <- respop %>%
  mutate(num_bins = lengths(st_covers(respop, rebin)))

left_side  <- st_bbox(rebin)$xmin
top_side <- st_bbox(rebin)$ymax

mydorm <- respop%>% filter(Name=="BEDOK")

my_bin <- rebin[mydorm,]

rebin <- rebin %>%
  st_join(my_bin) %>%
   mutate(by_me = !is.na(Name.y))

n_my_bin <- sum(rebin$by_me)

n_bin <- length(rebin$by_me)

pct_my_bins <- n_my_bin/ n_bin

ggplot(respop) +
  geom_sf(color = NA, 
          aes(fill = num_bins)) +
  scale_fill_viridis_c(name = "Singapore neighborhood\n by number of recyclebins",
                       breaks = breaks <- seq(0, 900, by = 100),
                       labels = paste(prettyNum(breaks, big.mark = ","),
                                      "bins")) +
  geom_sf(data=mydorm,fill=NA,color="red")+
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
   annotate(geom = "text", x = left_side, 
           y = top_side, 
           label = paste("Of the ", 
                         prettyNum(n_bin, big.mark = ","),
                         "recycle bins in Singapore, ", 
                         prettyNum(n_my_bin, big.mark = ","),
                         " (", 
                         prettyNum(100*pct_my_bins, digits = 0),
                         "%) are within my neighborhood.",
                         sep = ""),
           hjust = 0, vjust = 0, size = 3) +
theme_map() +
  theme(legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))
```
</br>
</br>
3. The number of skyline greeneries in the tree conservation area.
</br>
</br>
```{r}
treec <- treec %>%
  mutate(num_sky = lengths(st_covers(treec, skylinegreen1)))

left_side  <- st_bbox(skylinegreen1)$xmin
top_side <- st_bbox(skylinegreen1)$ymax

n_skyl <- skylinegreen1[treec,]

skylinegreen1 <- skylinegreen1 %>%
  st_join(n_skyl) %>%
   mutate(by_tc = !is.na(Name.y))

a <- sum(skylinegreen1$by_tc)

b <- length(skylinegreen1$by_tc)

c <- a/ b

ggplot(respop) +
  geom_sf(color = NA, 
          fill="lightgray") +
  geom_sf(data=treec,fill="lightgreen")+
    geom_sf(data = skylinegreen1, size = 0.01,
          aes(color = by_tc))+
  scale_color_manual(values = c("blue", "yellow"),
          name = "Singapore skyline greeneries by or not in tree conservation area", 
          labels = c("Skyline green not in TCA",
                     "Skyline green in TCA")) +
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
   annotate(geom = "text", x = left_side, 
           y = top_side, 
           label = paste("Of the ", 
                         prettyNum(b, big.mark = ","),
                         "skyline greens in Singapore, ", 
                         prettyNum(a, big.mark = ","),
                         " (", 
                         prettyNum(100*c, digits = 0),
                         "%) are in the Tree Conservation Area.",
                         sep = ""),
           hjust = 0, vjust = 0, size = 3) +
theme_map() +
  theme(legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))
```
</br>
</br>
4. The number of neighborhoods overlapping with TCA.
</br>
</br>
```{r, message=F}
respop <- respop %>%
  mutate(num_tca = lengths(st_overlaps(respop, treec))) %>%
  mutate(has_tca = num_tca > 0)

n_tca_nhoods <- sum(respop$has_tca)

n_tca_nhoods

left_side  <- st_bbox(respop)$xmin
top_side <- st_bbox(respop)$ymax

ggplot(respop) +
  geom_sf(fill = "lightgrey", aes(fill=has_tca)) +
  scale_fill_manual(values = c("cornsilk1", "darkseagreen1"),
          name = "Singapore Neighborhoods\nby presence of a TCA", 
          labels = c("Neighborhood without\nan overlapping tca",
                     "Neighborhood with an\noverlapping TCA")) +
  geom_sf(data=treec, fill="lightgreen", alpha=0.4)+
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
  annotate(geom = "text", x = left_side, 
           y = top_side - 1000, 
           label = paste(n_tca_nhoods ,
                         "of Singapore's", 
                         length(respop$Name),
                         "neighborhoods contain\nor overlap with", 
                         "TCA."),
           hjust = 0, vjust = 0, size = 3) +
  theme_map() +
  theme(panel.background = element_rect(fill = "white"),
        legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))

```

</br>
</br>
5. The number of neighborhoods overlapping with PARK.
</br>
</br>
```{r, message=F}
respop <- respop %>%
  mutate(num_tca = lengths(st_overlaps(respop, park))) %>%
  mutate(has_tca = num_tca > 0)

n_p_nhoods <- sum(respop$has_tca)

left_side  <- st_bbox(respop)$xmin
top_side <- st_bbox(respop)$ymax

ggplot(respop) +
  geom_sf(fill = "lightgrey", aes(fill=has_tca),alpha=0.5) +
  scale_fill_manual(values = c("cornsilk1", "darkseagreen1"),
          name = "Singapore Neighborhoods\nby presence of a park", 
          labels = c("Neighborhood without\nan overlapping park",
                     "Neighborhood with an\noverlapping park")) +
  geom_sf(data=park, fill="darkgreen", alpha=0.4)+
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
  annotate(geom = "text", x = left_side, 
           y = top_side - 1000, 
           label = paste(n_p_nhoods ,
                         "of Singapore's", 
                         length(respop$Name),
                         "neighborhoods contain\nor overlap with", 
                         "a park."),
           hjust = 0, vjust = 0, size = 3) +
  theme_map() +
  theme(panel.background = element_rect(fill = "white"),
        legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))

```

</br>
</br>
6. average density of recycle bins in neighborhood
</br>
</br>

```{r, message=F}
num_bins <-length(rebin1$Name)
respop <- respop%>%
  mutate(area = set_units(st_area(respop), km^2)) %>%
  mutate(recycle = as.numeric(num_bins / area))

ggplot(respop) +
  geom_sf(color = NA, 
          aes(fill = recycle)) +
    scale_fill_viridis_c(name = 
                           "Singapore neighborhood recycle bin density",
                       breaks = breaks <- seq(0, 15000, by = 1500),
                       labels = paste(prettyNum(breaks, big.mark = ","),
                                      "bins per square km"), direction = -1) +
  annotation_scale(location = "br") +
  annotation_north_arrow(location = "tr",
                         style = north_arrow_minimal()) +
theme_map() +
  theme(legend.position = "left",
    legend.background = element_rect(fill = alpha("white", 0.5), 
                                         color = "gray"))
```
